Validation of Visual Statistical Inference, with Application to Linear Models

### 2012-02-11 paper_jasa.tex
new figure added

Thus the density of $p_B$ is Uniform(0,1)  under $H_0$. As noted by \cite{Ruppert:2007} the density $$f_{P_B}(p_B; \delta)= \frac{f_{|t|}(F_{|t|}^{-1}(1-p_B);\delta)}{f_{|t|}(F_{|t|}^{-1}(1-p_B))}$$ derived from equation \ref{dist_p}  is a right skewed distribution under $H_1$.  In a lineup plot we simulate $m-1$ residual data sets from null model where each of these $m-1$ null data sets produces a corresponding $p$-value $p_{0,i}$ and $p_{0,i} \sim \text{Uniform}(0,1)$ for $i = 1, ..., m-1$. Suppose  $p_0=\min_i(p_{0,i})$. Thus $p_0 \sim \text{Beta}(1,m-1)$.

@@

>>>>

Thus the density of $p_B$ is Uniform(0,1)  under $H_0$. As noted by \cite{Ruppert:2007}, under $H_1$ the density $$f_{P_B}(p_B; \delta)= \frac{f_{|t|}(F_{|t|}^{-1}(1-p_B);\delta)}{f_{|t|}(F_{|t|}^{-1}(1-p_B))}$$ derived from equation \ref{dist_p}  is a right skewed distribution.  In a lineup plot we simulate $m-1$ residual data sets from null model where each of these $m-1$ null data sets produces a corresponding $p$-value $p_{0,i}$ and $p_{0,i} \sim \text{Uniform}(0,1)$ for $i = 1, ..., m-1$. Suppose  $p_0=\min_i(p_{0,i})$. Thus $p_0 \sim \text{Beta}(1,m-1)$.

@@

\begin{figure*}[hbtp]
   \centering
       \scalebox{0.7}{\includegraphics{power_loess_exp1.pdf}}
       \caption{Observed power shown by loess smoother with simultaneous bootstrap confidence band and the power of UMP test for sample size $n= 100,300$ and $\sigma = 12,5$ as per experiment 1.}
       \label{fig:power_loess1}
\end{figure*}

\begin{figure*}[hbtp]
   \centering
       \scalebox{0.7}{\includegraphics{power_loess_exp2.pdf}}
       \caption{Observed power shown by loess smoother with simultaneous bootstrap confidence band and the power of UMP test for sample size $n= 100,300$ and $\sigma = 12,5$ as per experiment 2.}
       \label{fig:power_loess2}
\end{figure*}
